---
title: "model_details"
author: "Ayesha Perera"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{model_details}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Far)
```

# Description

This imports and generates summary on fatal accidents based on data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System. Data source: [Fatality Analysis Reporting System (FARS)](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS))

## Load Packages
```{r}
library(Far)
```

## Load Data

The package includes some datasets as follows
```{r}
list.files(system.file("extdata", package = "Far"))
```

## Package Functions

### Function `make_filename`
The `make_filename(year)` function accepts a numerical value such as 2013, 2014, 2015. It'll then output the concatenated file name as 'accident_year.csv.bz2', etc.
```{r}
make_filename(2013)
```

### Function `fars_read`
Accepts a csv file and output it as a dataframe
```{r}
df_fars <- fars_read("accident_2015.csv.bz2")
head(df_fars, 3)
```

### Function `fars_read_years`
This function returns MONTH column of each year as a combined list. Input should be 2013, 2014, 2015, otherwise the function will generate an error message
This function uses `make_file_name` and `fars_read` as ancillary functions.

```{r}
fars_read_years(2013:2015)
```

### Function `fars_summarize_years`
This function returns the number of total fatal accident per month in 2013, 2014, 2015 respectively. It uses fars_read as ancillary functions.

```{r}
df_sum <- fars_summarize_years(2013:2015)
df_sum
```

### Function `fars_map_state`

```{r}
fars_map_state(state.num = 30, year = 2013)
```
